Useful R tidbits: Machine Learning

### 2022-02-09 _academics/ms797-useful-r-tidbits/ms797-useful-r-tidbits.Rmd
couple of tweaks

XXX
<hr>

@@

In order to fit a multiple linear regression model using least squares, we again use the `lm()` function. The syntax {\R{lm(y $\sim$ x1 + x2 + x3)}} is used to fit a model with three predictors, `x1`, `x2`, and `x3`.
The `summary()` function now outputs the regression coefficients for all the predictors.

@@

It is easy to include interaction terms in a linear model using the `lm()` function. The syntax `lstat:black` tells `R` to include an interaction term between `lstat` and `black`.
The syntax `lstat * age` simultaneously includes `lstat`, `age`, and the interaction term `lstat`$\times$`age` as predictors; it is a shorthand for `lstat + age + lstat:age`.
  %We can also pass in transformed versions of the predictors.

>>>>

# EVERYTHING BELOW THIS LINE

is direct paste from the book's sources which I have not yet written in my own words or added anything to. Stay tuned.

<hr />

@@

In order to fit a multiple linear regression model using least squares, we again use the `lm()` function. The syntax `lm(y ~ x1 + x2 + x3)` is used to fit a model with three predictors, `x1`, `x2`, and `x3`.
The `summary()` function now outputs the regression coefficients for all the predictors.

@@

It is easy to include interaction terms in a linear model using the `lm()` function. The syntax `lstat:black` tells `R` to include an interaction term between `lstat` and `black`.
The syntax `lstat * age` simultaneously includes `lstat`, `age`, and the interaction term `lstat`$\times$`age` as predictors; it is a shorthand for `lstat + age + lstat:age`.
